Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices

### 2018-05-23 Meetings/23.05.2018.mst1tfm/mst1tfm_topic21_vianello.tex
Update to TeX MST1TFM 23.05.18

\begin{frame}{Neutral behavior investigation on AUG}
  \only<1>{
    \begin{columns}
      \begin{column}{0.5\textwidth}
        \begin{itemize}
          \item Light emission analysis performed using 2 absolute
            calibrated CCD cameras with D$_{\alpha}$ and D$_{\gamma}$
            filter
          \item Tomographic inversion using pixel technique assuming
            emission only outside the LCFS and neglecting reflection
          \item Inversion technique based on \textbf{S}imultaneous \textbf{A}lgebraic
            \textbf{R}econstruction \textbf{T}echnique (SART) with no
            input from equilibrium and no regolarization
          \item Evolution during density ramp explored
        \end{itemize}
      \end{column}
      \begin{column}{0.5\textwidth}
        \includegraphics[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig1.pdf}
      \end{column}
    \end{columns}
  }
  \only<2>{
    \centering{\includegraphics[width=10cm]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig2.pdf}}

    \vspace{1cm}

    At the beginning of the fueling ramp emission localized in the HFS
  }
  \only<3>{
    \centering{\includegraphics[width=10cm]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig3.pdf}}

    \vspace{1cm}

Radiation starts moving along the separatrix with different patterns between the two radiation
  }
  \only<4>{
    \centering{\includegraphics[width=10cm]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig4.pdf}}

    \vspace{1cm}

@@

  \vspace{1cm}

>>>>

\begin{frame}{Neutral behavior investigation on AUG}
  \only<1>{
    \begin{columns}
      \begin{column}{0.5\textwidth}
        \begin{itemize}
          \item Light emission analysis performed using 2 absolute
            calibrated CCD cameras with D$_{\alpha}$ and D$_{\gamma}$
            filter
          \item Tomographic inversion using pixel technique assuming
            emission only outside the LCFS and neglecting reflection
          \item Inversion technique based on \textbf{S}imultaneous \textbf{A}lgebraic
            \textbf{R}econstruction \textbf{T}echnique (SART) with no
            input from equilibrium and no regolarization
          \item Evolution during density ramp explored
        \end{itemize}
      \end{column}
      \begin{column}{0.5\textwidth}
      \includegraphics[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig1.pdf}
    \end{column}
    \end{columns}
  }
  \only<2>{
    \begin{center}
    \begin{tikzonimage}[width=10cm]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig2.pdf}
        \node at (0.05, -0.02) {\textbf{D$_{\alpha}$}};
        \node at (0.6, -0.02) {\textbf{D$_{\gamma}$}};
      \end{tikzonimage}
    \end{center}

    At the beginning of the fueling ramp emission localized in the HFS
  }
  \only<3>{
    \begin{center}
    \begin{tikzonimage}[width=10cm]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig3.pdf}
        \node at (0.05, -0.02) {\textbf{D$_{\alpha}$}};
        \node at (0.6, -0.02) {\textbf{D$_{\gamma}$}};
      \end{tikzonimage}
    \end{center}

Radiation starts moving towards the X-point (different patterns D$_{\alpha}$, D$_{\gamma}$)
  }
  \only<4>{
    \begin{center}
    \begin{tikzonimage}[width=10cm]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig4.pdf}
        \node at (0.05, -0.02) {\textbf{D$_{\alpha}$}};
        \node at (0.6, -0.02) {\textbf{D$_{\gamma}$}};
      \end{tikzonimage}
    \end{center}

@@
